%-------------------------
% Resume in Latex
% Author : B. Munyoki Kilyungi
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
  {#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[4]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
    \small#3 & #4 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
  \textbf{\Huge \scshape Munyoki Kilyungi} \\ \vspace{1pt}
  \href{mailto:me [at] bonfacemunyoki [dot] com}{\underline{me [at] bonfacemunyoki [dot] com}} $|$ \href{https://bonfacemunyoki.com}{\underline{bonfacemunyoki.com}} $|$ \href{https://github.com/BonfaceKilz}{\underline{github:BonfaceKilz}} \\
  \small mobile:\underline{+254~797~111~111}
\end{center}

Research software developer who is deeply committed to the principles of the free software community and is passionate about GNU/Linux, functional programming, meta-programming, software packaging, reproducible builds/deployments, system design and empowering minorities in technology.


%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
      \textbf{Languages (advanced)}{: Python, GNU Guile, Common Lisp, Elisp} \\
      \textbf{Programming Languages (basic):} Javascript, Haskell, Racket\\
      \textbf{Developer Tools}{: GNU Emacs, Git, GNU/Linux, GNU Guix, Org-mode, FreeBSD, \LaTeX}
  }}
\end{itemize}


%-----------EXPERIENCE-----------
\section{Professional Experience}

\resumeSubHeadingListStart

\resumeSubheading
    {Research Software Engineer}{Mar. 2020 -- Present}
    {GeneNetwork}{\url{https://genenetwork.org}}

    \resumeItemListStart
    \resumeItem{Integrate RDF+LMDB into the \textit{GeneNetwork} Ecosystem by: creating an infrastructure implemented in GNU Guile, Python3 and Common Lisp for easily adding ad-hoc data in a way that is easily shareable to other labs globally in a semantic and FAIR way: \href{https://github.com/genenetwork/dump-genenetwork-database/}{\underline{RDF Dump}} and \href{https://github.com/BonfaceKilz/gn-dataset-dump/}{\underline{Common Lisp LMDB Matrix}}}
    \resumeItem{Maintain \href{https://github.com/genenetwork/genenetwork2}{\underline{Genenetwork2}}: continuously refactor the code base to improve it's quality; add new features requested by the project's stake holders; review, approve, and merge submitted Pull Requests.}
    
    \resumeItem{Maintain \href{https://github.com/genenetwork/genenetwork3}{\underline{Genenetwork3}} REST API written in Python3 for data science and machine learning to make it more accessible to researchers in the systems genetics space: Move key logic from the archived genenetwork1 \href{https://github.com/genenetwork/genenetwork1}{\underline{code-base}}; remodel some aspects of our data model; create endpoints that perform genetics computations; review, approve, and merge submitted pull requests.}

    \resumeItem{Help research, maintain, and upstream deterministic builds of \textit{GeneNetwork}-relevant packages for GNU Guix written in GNU Guile: \href{https://gitlab.com/genenetwork/guix-bioinformatics}{\underline{guix-bioinformatics}}}
    
    \resumeItem{Help organise webinars/presentations organised by the Genenetwork group e.g. \href{https://libreplanet.org/wiki/FOSDEM2021-devroom-declarative-and-minimalistic-computing}{\underline{FOSDEM 2021}} and \href{https://libreplanet.org/wiki/FOSDEM2023-devroom-proposal}{\underline{FOSDEM 2023}}}

    \resumeItemListEnd      

\resumeSubheading
    {Software Engineer}{Nov. 2018 -- Nov. 2019}
    {PlayCo Technology (Formerly knows as Sibsco)}{\url{https://shabiki.com}}
    \resumeItemListStart

    \resumeItem{Designed, tested and implemented features requested by the Products team with an emphasis on usability(customer-oriented), maintainability and scalability: Implemented mock-ups created by the Products/ Design team that targetted low end phones that ran on Opera Mini; Trouble-shot slow operations, more-so when customers wanted to review their purchase history; Created a static site generator that displayed relevant information to customers from a spreadsheet that was maintained in-house by a separate team.}
    
    \resumeItem{Deployment, integration(M-Pesa/ SMS), maintenance and automation of core fin-tech platform: Helped to write and test out Ansible deployment scripts; Helped adopt the then relatively new REST M-Pesa Daraja API; Trouble-shot production bugs that were related to either the existing SMS or M-Pesa integration; Reviewed submitted PR’s to reduce any complexity that existed in the code base.}
    
    \resumeItem{Support Work: maintained bulk messaging service in addition to sending them(bulk messages) out.}

    \resumeItemListEnd

\resumeSubheading
    {Software Engineer}{Nov. 2017 -- Jan. 2019}
    {Clinton Health Access Initiative}{\url{https://clintonhealthaccess.org}}
    \resumeItemListStart

    \resumeItem{Refactored and introduced automated testing to the Family Planning Project. Improved code coverage by about 47\% from zero.}
    \resumeItem{Introduced CI/ CD pipelines to the Family Planning Projects.}
    \resumeItem{Initiated documentation for the Family Planning Project: Wrote and regularly updated standard operating procedures for the team's internal processes, authored a comprehensive developer guide for setting up and troubleshooting the Family Planning Project and documented release procedures for the Family Planning Project.}
    \resumeItem{Worked with the global team to onboard new developers by: providing an overview of the projects we were working on in the form of presentations, documents and discussions; providing access to the available resources (E.g. servers); and providing guidance and support during the first few weeks, usually through pairing.}
    \resumeItemListEnd
\clearpage
\resumeSubheading
    {Co-founder}{Jul. 2013 -- Dec. 2016}
    {Angstrom (Now \textbf{Studio Aurum})}{\url{https://www.behance.net/angstrom_ke} or \url{https://aurum.studio/}}
    \resumeItemListStart

    \resumeItem{Researched and gained understanding of the market, target audience and product that any communication was aimed at.}
    \resumeItem{Assisted in designing and creating design briefs for apps and artwork as dictated by the company's clients.}
    \resumeItem{Co-ordinated website projects with the UX team or outside agencies.}
    \resumeItem{Brainstormed and created mock-ups of design ideas.}
    \resumeItem{Recommended tooling and stacks to be used by clients based on their needs.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------GRANTS-----------
\section{Grants}
\resumeSubHeadingListStart
\resumeProjectHeading
    {\textbf{Unlocking Biomedical Data for AI Health Research in Africa Using}}{}
    {\textbf{GeneNetwork as an Example}}{Sep. 2022 -- Sep. 2023}
    \resumeItemListStart
    \resumeItem{\textbf{Funding Organization:} Data Science Africa  (\url{https://www.datascienceafrica.org/})}
    \resumeItem{\textbf{Amount Awarded:} USD 5,000}
    \resumeItem{\textbf{Period of Grant Award:} 12 months}
    \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
    {Strathmore University}{Nairobi, Kenya}
    {MSc. Data Science and Analytics, Strathmore University}{May 2021 -- Current}
\resumeSubheading
    {University of Nairobi}{Nairobi, Kenya}
    {BSc. Electrical and Electronics Engineering}{2013 -- 2018}
\resumeSubheading
    {Mang'u High School}{Thika, Kenya}
    {KCSE}{2008 -- 2011}
\resumeSubHeadingListEnd    

\end{document}
